---
title: "covid_vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{covid_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(covid19data)
```

### active_cases(provinceName = 'Canada')

```{r}
data <- active_cases(provinceName = 'British Columbia')
head(data)
```

### vaccine_as_per_province(provinceName = 'Canada')

```{r}
data <- vaccine_as_per_province(provinceName = 'British Columbia')
head(data)
```

### cases_as_per_province(provinceName = 'Canada')

```{r}
data <- cases_as_per_province(provinceName = 'British Columbia')
head(data)
```

### Yearlycases_as_per_province(provinceName = 'Canada',yearpassed='2020')

```{r}
data <- Yearlycases_as_per_province(provinceName = 'British Columbia')
head(data)
```


### cumulativevaccine_as_per_province(provinceName = 'Canada')

```{r}
data <- cumulativevaccine_as_per_province(provinceName = 'British Columbia')
head(data)
```


### vaccine_distribution(provinceName = 'Canada')

```{r}
data <- vaccine_distribution(provinceName = 'British Columbia')
head(data)
```


### yearly_vaccine_distribution(provinceName = 'Canada',distyear='2020')

```{r}
data <- yearly_vaccine_distribution(provinceName = 'British Columbia', distyear = '2021')
head(data)
```


### mortality(provinceName = 'Canada')

```{r}
data <- mortality(provinceName = 'British Columbia')
head(data)
```


### yearly_deaths(provinceName = 'Canada', dyear='2020')

```{r}
data <- yearly_deaths(provinceName = 'British Columbia')
head(data)
```


### recovered(provinceName = 'Canada')

```{r}
data <- recovered(provinceName = 'British Columbia')
head(data)
```


### yearly_recovered(provinceName = 'Canada', ryear='2020')

```{r}
data <- yearly_recovered(provinceName = 'British Columbia', ryear='2020')
head(data)
```


### testing(provinceName = 'Canada')

```{r}
data <- testing(provinceName = 'British Columbia')
head(data)
```


### summary_of_cases(provinceName = "Canada")

```{r}
data <- summary_of_cases(provinceName = 'British Columbia')
head(data)
```


### summary_of_peaktime(provinceName = "Canada", date = '01-09-2020')

```{r}
data <- summary_of_peaktime(provinceName = 'British Columbia')
head(data)
```


### summary_of_canada(date = '01-09-2020')

```{r}
data <- summary_of_canada()
head(data)
```

### province_population(provinceName = 'Canada')

```{r}
data <- province_population()
head(data)
```















